Through the eyes of the teacher - Multimodal exploration of expertise differences in the perception of classroom disruptions in a laboratory study

### 2025-01-15 02_paper/02_study/02_expertise_paper/old R scripts/expertise_2024_09_26_no_outlierdetection_MK.tex
update

{
\setcounter{tocdepth}{2}
\tableofcontents
}
\subsection{1. Participants}\label{participants}

@@

\subsection{2. Measures}\label{measures}

\subsubsection{2.1 Eye-Tracking Data}\label{eye-tracking-data}

\paragraph{2.2.2 Letter search}\label{letter-search}

@@

\paragraph{2.2.1 Number of fixations per minute (micro-teaching
unit)}\label{number-of-fixations-per-minute-micro-teaching-unit}

@@

\paragraph{2.2.2 Number of fixations per minute (AOI
students)}\label{number-of-fixations-per-minute-aoi-students}

@@

\paragraph{2.2.2 Number of fixations per minute (AOI
others)}\label{number-of-fixations-per-minute-aoi-others}

@@

\paragraph{2.2.3 Number of fixations (AOI disruptive
person)}\label{number-of-fixations-aoi-disruptive-person}

@@

\paragraph{2.2.4 Average duration of fixations in milliseconds
(micro-teaching
unit)}\label{average-duration-of-fixations-in-milliseconds-micro-teaching-unit}

@@

\paragraph{2.2.5 Average duration of fixations (AOI
students)}\label{average-duration-of-fixations-aoi-students}

@@

\paragraph{2.2.6 Average duration of fixations (AOI disruptive
person)}\label{average-duration-of-fixations-aoi-disruptive-person}

@@

\paragraph{2.2.7 Gaze Relational Index (GRI; micro-teaching
unit)}\label{gaze-relational-index-gri-micro-teaching-unit}

@@

\paragraph{2.2.10 Time to first fixation in seconds (AOI disruptive
person)}\label{time-to-first-fixation-in-seconds-aoi-disruptive-person}

@@

\subsubsection{2.2 Rating Scales (Disruption Appraisal, Confidence
Appraisal, Prevalence
Rating)}\label{rating-scales-disruption-appraisal-confidence-appraisal-prevalence-rating}

@@

\section{\texorpdfstring{\texttt{\{r\ sri\_pr,\ echo=FALSE,\ message=FALSE,\ warning=FALSE,\ results=\textquotesingle{}asis\textquotesingle{}\}\ \#\ \ \#\ \#\#\#\#\#\#\#\#\#\#\#\#\#\#\ Prevalence\ Rating\ \#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\ \#\ \ \#\ sri.preva.table\ \textless{}-\ \#\ \ \ sri\ \%\textgreater{}\%\ \#\ \ \ group\_by(ID)\ \%\textgreater{}\%\ \#\ \ \ summarise(\ \#\ \ \ \ \ N\ =\ n(),\ \#\ \ \ \ \ "M"\ =\ round(mean(prevalence\_rating),\ digits\ =\ 2),\ \#\ \ \ \ \ "SD"\ =\ round(sd(prevalence\_rating),\ digits\ =\ 2),\ \#\ \ \ \ \ "Min"\ =\ min(prevalence\_rating),\ \#\ \ \ \ \ "Max"\ =\ max(prevalence\_rating)\ \#\ \ \ )\ \#\ \ \#\ \#\ insert\ a\ table\ into\ HTML\ \#\ knitr::kable(sri.preva.table,\ \#\ \ \ \ \ \ \ \ \ \ \ \ \ \ caption\ =\ "Prevalence\ rating")\ \#\ \ \#\ \#\#\#\#\ with\ event\ \ \#\ sri.preva.event.table\ \textless{}-\ \#\ \ \ sri\ \%\textgreater{}\%\ \#\ \ \ group\_by(ID,\ event)\ \%\textgreater{}\%\ \#\ \ \ summarise(\ \#\ \ \ \ \ N\ =\ n(),\ \#\ \ \ \ \ "M"\ =\ round(mean(prevalence\_rating),\ digits\ =\ 2),\ \#\ \ \ \ \ "SD"\ =\ round(sd(prevalence\_rating),\ digits\ =\ 2),\ \#\ \ \ \ \ "Min"\ =\ min(prevalence\_rating),\ \#\ \ \ \ \ "Max"\ =\ max(prevalence\_rating)\ \#\ \ \ )\ \#\ \ \#\ \#\ insert\ a\ table\ into\ HTML\ \#\ knitr::kable(sri.preva.event.table,\ \#\ \ \ \ \ \ \ \ \ \ \ \ \ \ caption\ =\ "Prevalence\ rating\ with\ events")\ \#\ \ \#\ \#\ create\ a\ new\ data\ frame\ with\ rating\ \#\ sri\_preva\ \textless{}-\ subset.data.frame(sri,\ select\ =\ c(ID,\ event,\ prevalence\_rating))\ \#\ \ \#\ \#\ plotting\ prevalence\ rating\ for\ groups\ \#\ preva\_group\_plot\ \textless{}-\ \ \#\ \ \ sri\_preva\ \%\textgreater{}\%\ \ \#\ \ \ mutate(ID\ =\ factor(ID,\ \#\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ levels\ =\ c("Novice",\ \#\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ "Expert"\ \#\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ )\ \#\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ )\ \#\ \ \ \ \ \ \ \ \ \ )\ \%\textgreater{}\%\ \ \#\ \ \ ggplot(mapping\ =\ aes(x\ =\ ID,\ \#\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ y\ =\ prevalence\_rating))\ +\ \#\ \ \ geom\_boxplot(mapping\ =\ aes(fill\ =\ ID),\ \#\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ outlier.shape\ =\ NA)\ +\ \#\ \ \ geom\_point(size\ =\ 1,\ \#\ \ \ \ \ \ \ \ \ \ \ \ \ \ alpha\ =\ 0.4,\ \#\ \ \ \ \ \ \ \ \ \ \ \ \ \ position\ =\ position\_jitter(seed\ =\ 1,\ \#\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ width\ =\ 0.1,\ \#\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ height\ =\ 0.1))\ +\ \#\ \ \ scale\_x\_discrete(limits\ =\ c("Novice",\ "Expert"))\ +\ \#\ \ \ scale\_y\_continuous(breaks\ =\ seq(from\ =\ 0,\ to\ =\ 10,\ by\ =\ 1))\ +\ \ \#\ \ \ labs(x\ =\ "",\ \#\ \ \ \ \ \ \ \ y\ =\ "Prevalence\ Rating")\ +\ \ \#\ \ \ scale\_fill\_brewer(palette\ \ =\ "RdBu")\ +\ \ \ \#\ \ \ ggtitle("How\ widespread\ is\ this\ event\ in\ the\ classroom?")\ +\ \#\ \ \ theme\_cowplot()\ \#\ \ \#\ preva\_group\_plot\ \#\ \ \#}}{\{r sri\_pr, echo=FALSE, message=FALSE, warning=FALSE, results=\textquotesingle asis\textquotesingle\} \#  \# \#\#\#\#\#\#\#\#\#\#\#\#\#\# Prevalence Rating \#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\# \#  \# sri.preva.table \textless- \#   sri \%\textgreater\% \#   group\_by(ID) \%\textgreater\% \#   summarise( \#     N = n(), \#     "M" = round(mean(prevalence\_rating), digits = 2), \#     "SD" = round(sd(prevalence\_rating), digits = 2), \#     "Min" = min(prevalence\_rating), \#     "Max" = max(prevalence\_rating) \#   ) \#  \# \# insert a table into HTML \# knitr::kable(sri.preva.table, \#              caption = "Prevalence rating") \#  \# \#\#\#\# with event  \# sri.preva.event.table \textless- \#   sri \%\textgreater\% \#   group\_by(ID, event) \%\textgreater\% \#   summarise( \#     N = n(), \#     "M" = round(mean(prevalence\_rating), digits = 2), \#     "SD" = round(sd(prevalence\_rating), digits = 2), \#     "Min" = min(prevalence\_rating), \#     "Max" = max(prevalence\_rating) \#   ) \#  \# \# insert a table into HTML \# knitr::kable(sri.preva.event.table, \#              caption = "Prevalence rating with events") \#  \# \# create a new data frame with rating \# sri\_preva \textless- subset.data.frame(sri, select = c(ID, event, prevalence\_rating)) \#  \# \# plotting prevalence rating for groups \# preva\_group\_plot \textless-  \#   sri\_preva \%\textgreater\%  \#   mutate(ID = factor(ID, \#                      levels = c("Novice", \#                                 "Expert" \#                                 ) \#                      ) \#          ) \%\textgreater\%  \#   ggplot(mapping = aes(x = ID, \#                        y = prevalence\_rating)) + \#   geom\_boxplot(mapping = aes(fill = ID), \#                outlier.shape = NA) + \#   geom\_point(size = 1, \#              alpha = 0.4, \#              position = position\_jitter(seed = 1, \#                                         width = 0.1, \#                                         height = 0.1)) + \#   scale\_x\_discrete(limits = c("Novice", "Expert")) + \#   scale\_y\_continuous(breaks = seq(from = 0, to = 10, by = 1)) +  \#   labs(x = "", \#        y = "Prevalence Rating") +  \#   scale\_fill\_brewer(palette  = "RdBu") +   \#   ggtitle("How widespread is this event in the classroom?") + \#   theme\_cowplot() \#  \# preva\_group\_plot \#  \#}}\label{r-sri_pr-echofalse-messagefalse-warningfalse-resultsasis-prevalence-rating-sri.preva.table---sri-group_byid-summarise-n-n-m-roundmeanprevalence_rating-digits-2-sd-roundsdprevalence_rating-digits-2-min-minprevalence_rating-max-maxprevalence_rating-insert-a-table-into-html-knitrkablesri.preva.table-caption-prevalence-rating-with-event-sri.preva.event.table---sri-group_byid-event-summarise-n-n-m-roundmeanprevalence_rating-digits-2-sd-roundsdprevalence_rating-digits-2-min-minprevalence_rating-max-maxprevalence_rating-insert-a-table-into-html-knitrkablesri.preva.event.table-caption-prevalence-rating-with-events-create-a-new-data-frame-with-rating-sri_preva---subset.data.framesri-select-cid-event-prevalence_rating-plotting-prevalence-rating-for-groups-preva_group_plot---sri_preva-mutateid-factorid-levels-cnovice-expert-ggplotmapping-aesx-id-y-prevalence_rating-geom_boxplotmapping-aesfill-id-outlier.shape-na-geom_pointsize-1-alpha-0.4-position-position_jitterseed-1-width-0.1-height-0.1-scale_x_discretelimits-cnovice-expert-scale_y_continuousbreaks-seqfrom-0-to-10-by-1-labsx-y-prevalence-rating-scale_fill_brewerpalette-rdbu-ggtitlehow-widespread-is-this-event-in-the-classroom-theme_cowplot-preva_group_plot}

\paragraph{t-Test \& effect size ``Prevalence
rating''}\label{t-test-effect-size-prevalence-rating}

\section{\texorpdfstring{\texttt{\{r\ sri\_pr\_ttest,\ echo=FALSE,\ message=FALSE,\ warning=FALSE,\ results=\textquotesingle{}asis\textquotesingle{}\}\ \#\ \ \#\ \#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\ T-TEST\ \&\ EFFECT\ SIZE\ \#\#\#\#\#\#\#\#\#\#\#\#\ \#\ \ \#\ \#\ Prevalence\ Rating\ \ \#\ \#\ t-test\ for\ expertise\ differences\ \#\ t.test(x\ =\ sri\$prevalence\_rating{[}sri\$ID\ ==\ "Expert"{]},\ \#\ \ \ \ \ \ \ \ y\ =\ sri\$prevalence\_rating{[}sri\$ID\ ==\ "Novice"{]},\ \#\ \ \ \ \ \ \ \ var.equal\ =\ TRUE)\ \#\ \ \#\ \#\ Prevalence\ Rating\ \ \#\ \#\ effect\ size\ for\ expertise\ differences\ \#\ d\_sri\_preva\ \textless{}-\ CohenD(x\ =\ sri\$prevalence\_rating{[}sri\$ID\ ==\ "Expert"{]},\ \#\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ y\ =\ sri\$prevalence\_rating{[}sri\$ID\ ==\ "Novice"{]},\ \#\ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ na.rm\ =\ TRUE)\ \#\ \ \#\ round(d\_sri\_preva,\ 2)\ \#\ \ \#}}{\{r sri\_pr\_ttest, echo=FALSE, message=FALSE, warning=FALSE, results=\textquotesingle asis\textquotesingle\} \#  \# \#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\#\# T-TEST \& EFFECT SIZE \#\#\#\#\#\#\#\#\#\#\#\# \#  \# \# Prevalence Rating  \# \# t-test for expertise differences \# t.test(x = sri\$prevalence\_rating{[}sri\$ID == "Expert"{]}, \#        y = sri\$prevalence\_rating{[}sri\$ID == "Novice"{]}, \#        var.equal = TRUE) \#  \# \# Prevalence Rating  \# \# effect size for expertise differences \# d\_sri\_preva \textless- CohenD(x = sri\$prevalence\_rating{[}sri\$ID == "Expert"{]}, \#                       y = sri\$prevalence\_rating{[}sri\$ID == "Novice"{]}, \#                       na.rm = TRUE) \#  \# round(d\_sri\_preva, 2) \#  \#}}\label{r-sri_pr_ttest-echofalse-messagefalse-warningfalse-resultsasis-t-test-effect-size-prevalence-rating-t-test-for-expertise-differences-t.testx-sriprevalence_ratingsriid-expert-y-sriprevalence_ratingsriid-novice-var.equal-true-prevalence-rating-effect-size-for-expertise-differences-d_sri_preva---cohendx-sriprevalence_ratingsriid-expert-y-sriprevalence_ratingsriid-novice-na.rm-true-roundd_sri_preva-2}

@@

\subsubsection{2.3 Situational Jugdement
Test}\label{situational-jugdement-test}

@@

\subsubsection{2.4 Classroom
Questionnaire}\label{classroom-questionnaire}

@@

\subsection{3. Correlations}\label{correlations}

>>>>

{
\setcounter{tocdepth}{2}
\tableofcontents
}
\subsection{Participants}\label{participants}

@@

\subsection{Measures}\label{measures}

\subsubsection{Eye-Tracking Data}\label{eye-tracking-data}

\paragraph{Letter search}\label{letter-search}

@@

\paragraph{Number of fixations per minute (micro-teaching
unit)}\label{number-of-fixations-per-minute-micro-teaching-unit}

@@

\paragraph{Number of fixations per minute (AOI
students)}\label{number-of-fixations-per-minute-aoi-students}

@@

\paragraph{Number of fixations per minute (AOI
others)}\label{number-of-fixations-per-minute-aoi-others}

@@

\subsubsection{ALL AOIs}\label{all-aois}

\includegraphics{expertise_2024_09_26_no_outlierdetection_MK_files/figure-latex/nof_all_aois-1.pdf}

\paragraph{Number of fixations (AOI disruptive
person)}\label{number-of-fixations-aoi-disruptive-person}

@@

\paragraph{Average duration of fixations in milliseconds (micro-teaching
unit)}\label{average-duration-of-fixations-in-milliseconds-micro-teaching-unit}

@@

\paragraph{Average duration of fixations (AOI
students)}\label{average-duration-of-fixations-aoi-students}

@@

\paragraph{Average duration of fixations (AOI disruptive
person)}\label{average-duration-of-fixations-aoi-disruptive-person}

@@

\paragraph{Gaze Relational Index (GRI; micro-teaching
unit)}\label{gaze-relational-index-gri-micro-teaching-unit}

@@

\paragraph{Time to first fixation in seconds (AOI disruptive
person)}\label{time-to-first-fixation-in-seconds-aoi-disruptive-person}

@@

\subsubsection{Rating Scales (Disruption Appraisal, Confidence
Appraisal, Prevalence
Rating)}\label{rating-scales-disruption-appraisal-confidence-appraisal-prevalence-rating}

@@

\begin{longtable}[]{@{}lrrrrr@{}}
\caption{Prevalence rating}\tabularnewline
\toprule\noalign{}
ID & N & M & SD & Min & Max \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
ID & N & M & SD & Min & Max \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Expert & 352 & 6.53 & 2.72 & 1 & 10 \\
Novice & 357 & 7.02 & 2.20 & 1 & 10 \\
\end{longtable}

\begin{longtable}[]{@{}llrrrrr@{}}
\caption{Prevalence rating with events}\tabularnewline
\toprule\noalign{}
ID & event & N & M & SD & Min & Max \\
\midrule\noalign{}
\endfirsthead
\toprule\noalign{}
ID & event & N & M & SD & Min & Max \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Expert & chatting & 41 & 6.41 & 2.61 & 2 & 10 \\
Expert & clicking pen & 38 & 5.76 & 2.54 & 1 & 10 \\
Expert & drawing & 35 & 8.43 & 1.77 & 3 & 10 \\
Expert & drumming & 39 & 6.00 & 2.56 & 1 & 10 \\
Expert & head on table & 40 & 6.05 & 2.59 & 1 & 10 \\
Expert & heckling & 41 & 5.15 & 2.70 & 1 & 10 \\
Expert & looking at phone & 36 & 7.03 & 2.52 & 1 & 10 \\
Expert & snipping & 41 & 5.27 & 2.77 & 1 & 10 \\
Expert & whispering & 41 & 8.95 & 1.40 & 5 & 10 \\
Novice & chatting & 42 & 6.86 & 2.18 & 1 & 10 \\
Novice & clicking pen & 40 & 6.85 & 2.02 & 3 & 10 \\
Novice & drawing & 35 & 8.40 & 1.48 & 4 & 10 \\
Novice & drumming & 40 & 5.47 & 2.14 & 1 & 10 \\
Novice & head on table & 40 & 6.62 & 1.85 & 3 & 10 \\
Novice & heckling & 41 & 5.76 & 2.32 & 2 & 10 \\
Novice & looking at phone & 35 & 7.26 & 2.05 & 3 & 10 \\
Novice & snipping & 42 & 7.05 & 1.96 & 3 & 10 \\
Novice & whispering & 42 & 9.05 & 1.23 & 4 & 10 \\
\end{longtable}

\includegraphics{expertise_2024_09_26_no_outlierdetection_MK_files/figure-latex/sri_pr-1.pdf}
Two Sample t-test

data: sri\(prevalence_rating[sri\)ID == ``Expert''{]} and
sri\(prevalence_rating[sri\)ID == ``Novice''{]} t = -2.6154, df = 707,
p-value = 0.009103 alternative hypothesis: true difference in means is
not equal to 0 95 percent confidence interval: -0.8499891 -0.1210448
sample estimates: mean of x mean of y 6.534091 7.019608

{[}1{]} -0.2 attr(,``magnitude'') {[}1{]} ``negligible''

@@

\subsubsection{Situational Jugdement
Test}\label{situational-jugdement-test}

@@

\subsubsection{Classroom Questionnaire}\label{classroom-questionnaire}

@@

\subsection{Correlations}\label{correlations}
